### 2017-05-22 2017mergingmerges/section/01-Introduction.tex
Fix wibble in Intro

In this paper we present Machine Fusion, a new approach. Each operator is expressed as a restricted, sequential imperative program which \emph{pulls} from input streams, and \emph{pushes} to output streams. We view each operator as a process in a concurrent process network. Our fusion transform then \emph{sequentializes} the concurrent process network into a single process, by choosing a particular interleaving of the operator code that requires no unbounded intermediate buffers. When the fusion transform succeeds we know it has worked. There is no need to inspect intermediate representations of the compiler to debug poor performance, which is a common problem in systems based on general purpose program transformations \cite{lippmeier2012:guiding}.

>>>>

In this paper we present Machine Fusion, a new approach. Each operator is expressed as a restricted, sequential imperative program which \emph{pulls} from input streams, and \emph{pushes} to output streams. We view each operator as a process in a concurrent process network. Our fusion transform then \emph{sequentializes} the concurrent process network into a single process, by choosing a particular interleaving of the operator code that requires no unbounded intermediate buffers. When the fusion transform succeeds we know it has worked. There is no need to inspect intermediate representations of the compiled code to debug poor performance, which is a common problem in systems based on general purpose program transformations \cite{lippmeier2012:guiding}.
